humanCdGF_predict_cfu

### 2016-10-20 code/HumanCdGF_predict_cfu.Rmd
add leave 1 cage out for cfu

ggplot(data = rf_prediction, aes(x=observed, y=predicted, color = cage_id)) + geom_point() + 
  labs(x= 'Observed CFU (log10)', y = 'Predicted CFU (log10)',
       title = "Random Forest Prediction of Colonized C Difficile CFU from Day 0 Community") + 
  theme_bw() + xlim(0,9) + ylim(0,9) + 
  annotate('text', x=0.15*(max(rf_prediction$observed)), 
           y=0.95*(max(rf_prediction$predicted)), parse = T,
           label=paste0('R^2 == ', round(tail(rf_n_features$rsq, 1), 2))) + 
  theme(legend.position = 'none')

>>>>

##### - leave one cage out cv
LOcO_df <- data.frame(colonized_cfu %>% 
    right_join(community_d0.df) %>% 
    filter(!is.na(log_cfu_med)) %>% 
    select(log_cfu_med, cage_id, one_of(top_important_OTU)))
cage_list <- as.character(unique(LOcO_df$cage_id))

LOcO_probs <- c()
LOcO_rf <- c()
rsq <- c()
import_otus <- data.frame(otu = top_important_OTU)
for(i in 1:length(cage_list)){
  by_cage <- LOcO_df$cage_id == cage_list[i]
  LOcO_predict <- select(LOcO_df, -cage_id)
  train <- LOcO_predict[!by_cage,]
  test <- LOcO_predict[by_cage,]
  set.seed(seed)
  temp_model <- randomForest(log_cfu_med~., data=train, pdel=0.99, ntree=500)
  import_df <- importance(temp_model)
  colnames(import_df) <- cage_list[i]
  import_otus <- merge(import_otus, import_df, by.x = 'otu', by.y = 'row.names')
  rsq[i] <- round(tail(temp_model$rsq, 1), 2)
  LOcO_probs <- rbind(LOcO_probs, data.frame(cage=rep(cage_list[i], nrow(test)),
                                             actual=test$log_cfu_med, 
                                             pred=predict(temp_model, test)))
}
LOcO_roc <- roc(LOcO_df$Euth_Early~LOcO_probs)
##### - leave one cage out cv

ggplot(data = rf_prediction, aes(x=observed, y=predicted, color = cage_id)) + geom_point() + 
  labs(x= 'Observed CFU (log10)', y = 'Predicted CFU (log10)',
       title = "Random Forest Prediction of Colonized C Difficile CFU from Day 0 Community") + 
  theme_bw() + annotate('text', x=0.15*(max(rf_prediction$observed)), 
                        y=0.95*(max(rf_prediction$predicted)), parse = T,
                        label=paste0('R^2 == ', round(tail(rf_n_features$rsq, 1), 2))) + 
  theme(legend.position = 'none')
